Market simulator

### 2020-11-20 analysis/05_market_simulator.Rmd
minor edits
took out radioButtons

Market share
--------------------------------------

@@

Imports
--------------------------------------

```{r import}
# let the user choose the type of input file
radioButtons(
  inputId = "what_config",
  label = "Choose Configuration",
  choices = c("Default", "User input"),
  selected = "Default",
  inline = FALSE
  )

# Organization file input
conditionalPanel(condition = 'input.what_config == "User input"',
                 fileInput(
                   "org_update",
                   "Import Organization Data",
                   accept = c(
                     "text/csv",
                     "text/comma-separated-values,text/plain",
                     ".csv"
                   )
                  ),
                 actionButton(
                   "org_button",
                   label = "Update Organization Data"
                  )
                 )

# Persona file input
conditionalPanel(condition = 'input.what_config == "User input"',               
                fileInput(
                  "per_update",
                  "Import Persona Data",
                  accept = c(
                    "text/csv",
                    "text/comma-separated-values,text/plain",
                    ".csv"
                  )
                ),
                actionButton(
                  "per_button",
                  label = "Update Persona Data"
                )
              )

# Organization Configuration
organization_data <- reactive({
  if (input$what_config == "Default") {
    x <- org_default
  } else {
    if (input$what_config == "User input") {
      req(input$org_button)
      req(input$org_update)
      x <- read_csv(input$org_update$datapath)
    }
  }
})

# Persona Configuration
persona_data <- reactive({
  if (input$what_config == "Default") {
    x <- per_default
  } else {
    if (input$what_config == "User input") {
      req(input$per_button)
      req(input$per_update)
      x <- read_csv(input$per_update$datapath)
    }
  }
})

Configurations
--------------------------------------------------

@@

>>>>

Market share
-------------------------------------------------

@@

Configurations
-------------------------------------------------

@@

Import
-------------------------------------------------

```{r import}
# # let the user choose the type of input file
# radioButtons(
#   inputId = "what_config",
#   label = "Choose Configuration",
#   choices = c("Default", "Organization", "Persona"),
#   selected = "Default",
#   inline = FALSE
#   )

# Organization file input
# conditionalPanel(condition = 'input.what_config == "User input"',
#                  fileInput(
#                    "org_update",
#                    "Import Organization Data",
#                    accept = c(
#                      "text/csv",
#                      "text/comma-separated-values,text/plain",
#                      ".csv"
#                    )
#                   ),
#                  actionButton(
#                    "org_button",
#                    label = "Update Organization Data"
#                   )
#                  )

fileInput(
 "org_update",
 "Import Organization Data",
 accept = c(
   "text/csv",
   "text/comma-separated-values,text/plain",
   ".csv"
 )
)

actionButton(
 "org_button",
 label = "Update Organization Data"
)

# Persona file input
# conditionalPanel(condition = 'input.what_config == "User input"',               
#                 fileInput(
#                   "per_update",
#                   "Import Persona Data",
#                   accept = c(
#                     "text/csv",
#                     "text/comma-separated-values,text/plain",
#                     ".csv"
#                   )
#                 ),
#                 actionButton(
#                   "per_button",
#                   label = "Update Persona Data"
#                 )
#               )

fileInput(
  "per_update",
  "Import Persona Data",
  accept = c(
    "text/csv",
    "text/comma-separated-values,text/plain",
    ".csv"
  )
)
actionButton(
  "per_button",
  label = "Update Persona Data"
)

# Organization Configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    x <- org_default
  } else {
    req(input$org_button)
    req(input$org_update)
    x <- read_csv(input$org_update$datapath)
  }
})

# Persona Configuration
persona_data <- reactive({
  if (is.null(input$per_update$datapath)) {
    x <- per_default
  } else {
    req(input$per_button)
    req(input$per_update)
    x <- read_csv(input$per_update$datapath)
  }
})
